The Astropy Project:

### 2017-09-29 main.tex
add word new

\textbf{Key features:}
\begin{itemize}
	\item incl logarithmic units and magnitudes
	\item speed improvements
    \item interaction with numpy arrays
\end{itemize}

@@

- Three-tiered structure for coordinates: representation, frame, skycoord
- With differential classes, frames support velocities

@@

\textbf{Key features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
    \item Proper motions, radial velocities
\end{itemize}

>>>>

\textbf{Key new features:}
\begin{itemize}
	\item incl logarithmic units and magnitudes
	\item speed improvements
    \item interaction with numpy arrays
\end{itemize}

@@

The classes that handle coordinate representations (the \texttt{Representation}
classes) act like three-dimensional vectors and thus support vector arithmetic.

- With differential classes, frames support velocities

@@

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
    \item Proper motions, radial velocities
\end{itemize}
